The \dealii Library, Version 9.7

### 2025-08-14 9.7/paper.tex
Mention the Legacy::SolutionTransfer class.
Change a word.
Fix some minor grammar problems.

Finally, we have streamlined the interface of the functor invoked by the GPU
kernel. In the past, this interface included a cell index,
\texttt{Portable::MatrixFree::Data} (which includes precomputed data such as
quadrature points, shape functions, and other informations that needs to be
transferred to the GPU), and \texttt{Portable::MatrixFree::SharedData} (which
contained scratch memory used for computation). Now, all this information has
been consolidated into a single new class
\texttt{Portable::MatrixFree::Data}, greatly simplifying the interface.

@@

The 9.7 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_6_0_and_9_7_0.html}
     {around 25 incompatible changes};
see \cite{changes97}. Many of these
incompatibilities remove previously deprecated functions or classes,
or require now widely available but newer versions of external
dependencies than previous \dealii{} versions. Others
change internal
interfaces that are not usually used in external
applications. The following are worth mentioning since they
are more broadly visible:
\begin{itemize}
  \item The classes \texttt{Subscriptor} and \texttt{SmartPointer} have been
    renamed to \texttt{EnableObserverPointer} and \texttt{ObserverPointer}. Many
    core classes, such as \texttt{DoFHandler} and \texttt{Triangulation},
    inherit from \texttt{EnableObserverPointer} to enable other classes to store
    \texttt{ObserverPointer}s pointing to them which, if dereferenced after the
    pointed-to object goes out of scope, will signal an error that the
    pointer is now ``dangling''. This
    functionality has been in \dealii since 1998. Since ``smart pointers''
    nowadays typically refer to the \texttt{std::unique\_ptr} or
    \texttt{std::shared\_ptr} classes, these
    names were updated to avoid this conflict in terminology. The new names are
    based on the proposal for \texttt{std::observer\_ptr}~\cite{Brown2014} and
    \texttt{std::enable\_shared\_from\_this}.

>>>>

Finally, we have streamlined the interface of the functor invoked by the GPU
kernel. In the past, this interface included a cell index,
\texttt{Portable::MatrixFree::Data} (which includes precomputed data such as
quadrature points, shape functions, and other information that needs to be
transferred to the GPU), and \texttt{Portable::MatrixFree::SharedData} (which
contained scratch memory used for computation). Now, all this information has
been consolidated into a single new class
\texttt{Portable::MatrixFree::Data}, greatly simplifying the interface.

@@

The 9.7 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_6_0_and_9_7_0.html}
     {around 25 incompatible changes};
see \cite{changes97}. Many of these
incompatibilities remove previously deprecated functions or classes,
or require now widely available but newer versions of external
dependencies than previous \dealii{} versions. Others
change internal
interfaces that are not usually used in external
applications. The following are worth mentioning since they
are more broadly visible:
\begin{itemize}
  \item The classes \texttt{Subscriptor} and \texttt{SmartPointer} have been
    renamed to \texttt{EnableObserverPointer} and \texttt{ObserverPointer}. Many
    core classes, such as \texttt{DoFHandler} and \texttt{Triangulation},
    inherit from \texttt{EnableObserverPointer} to enable other classes to store
    \texttt{ObserverPointer}s pointing to them which, if dereferenced after the
    pointed-to object goes out of scope, will signal an error that the
    pointer is now ``dangling''. This
    functionality has been in \dealii since 1998. Since ``smart pointers''
    nowadays typically refers to the \texttt{std::unique\_ptr} or
    \texttt{std::shared\_ptr} classes, these
    names were updated to avoid this conflict in terminology. The new names are
    based on the proposal for \texttt{std::observer\_ptr}~\cite{Brown2014} and
    \texttt{std::enable\_shared\_from\_this}.
